The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-09-11 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Adding log N log S images
Small changes

\begin{table*}
\caption{List of observations used in the analyses. The RFI column contains the fraction of visibilities that the initial \textsc{aoflagger} run has detected (which includes false positives). The DVB column displays the fraction of visibilities that were unusable because of the presence of DVB signals. Because the DVB frequencies are only observed in GLEAM observations, this fraction is only given for those. }\label{tbl:obs-list}
\begin{tabular}{|l|l|r|r|r|c|}
\hline
\textbf{Project} &\textbf{Date} & \textbf{Frequencies (MHz)} & \textbf{Duration} & RFI & DVB \\
\hline
EoR   & 2013-08-23 & 138.8--197.7              & 3h & 0.53\% & ---\\
GLEAM & 2013-08-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.94\% & 0\% \\
EoR   & 2013-08-26 & 138.8--197.7              & 6h & 0.81\% & ---\\
GLEAM & 2013-11-05 & 72.3--133.8, 138.8--230.8 & 7h & 1.30\% & 0\% \\
GLEAM & 2013-11-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.69\% & 0\% \\
EoR   & 2014-02-05 & 138.8--197.7              & 6h & 0.54\% & -- \\
GLEAM & 2014-03-16 & 72.3--133.8, 138.8--230.8 & 7h & 0.79\% & 0\% \\
GLEAM & 2014-03-17 & 72.3--133.8, 138.8--230.8 & 7h & 1.64\% & 3\% \\
EoR   & 2014-04-10 & 138.8--197.7              & 6h & 0.68\% & ---\\
GLEAM & 2014-06-18 & 72.3--133.8, 138.8--230.8 & 7h & 0.98\% & 0\% \\
RFI test&2014-08-27& 131.2--161.9     & 2$\times$8 m& 1.85\% & --- \\
\hline
\multicolumn{3}{|r|}{\textbf{Total}} & \textbf{63h} & \textbf{0.97\%} & \textbf{0.5\%}\\
\hline
\end{tabular}
\end{table*}

@@

The GLEAM survey covers 72.3--230.8 MHz split into 5 bands of 30.72 MHz. Because the GLEAM observations are made in drift-scan mode, 5 subsequent snapshots observe all 5 bands.

@@

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/2014-03-17-dvb-stddevs}\vspace{-1cm}
\caption{..}
\label{fig:rfi-per-set}
\end{center}
\end{figure*}

>>>>

\begin{table*}
\caption{List of observations used in the analyses. The RFI column contains the fraction of visibilities that the initial \textsc{aoflagger} run has classified as RFI (which includes false positives). The DVB column displays the fraction of visibilities that were unusable because of the presence of DVB signals, and which the flagger does not flag. Because the DVB frequencies are only observed in GLEAM observations, this fraction is only given for those. }\label{tbl:obs-list}
\begin{tabular}{|l|l|r|r|r|c|}
\hline
\textbf{Project} &\textbf{Date} & \textbf{Frequencies (MHz)} & \textbf{Duration} & RFI & DVB \\
\hline
EoR   & 2013-08-23 & 138.8--197.7              & 3h & 0.53\% & ---\\
GLEAM & 2013-08-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.94\% & 0\% \\
EoR   & 2013-08-26 & 138.8--197.7              & 6h & 0.81\% & ---\\
GLEAM & 2013-11-05 & 72.3--133.8, 138.8--230.8 & 7h & 1.30\% & 0\% \\
GLEAM & 2013-11-25 & 72.3--133.8, 138.8--230.8 & 7h & 0.69\% & 0\% \\
EoR   & 2014-02-05 & 138.8--197.7              & 6h & 0.54\% & -- \\
GLEAM & 2014-03-16 & 72.3--133.8, 138.8--230.8 & 7h & 0.79\% & 0\% \\
GLEAM & 2014-03-17 & 72.3--133.8, 138.8--230.8 & 7h & 1.64\% & 3\% \\
EoR   & 2014-04-10 & 138.8--197.7              & 6h & 0.68\% & ---\\
GLEAM & 2014-06-18 & 72.3--133.8, 138.8--230.8 & 7h & 0.98\% & 0\% \\
RFI test&2014-08-27& 131.2--161.9     & 2$\times$8 m& 1.85\% & --- \\
\hline
\multicolumn{3}{|r|}{\textbf{Total}} & \textbf{63h} & \textbf{0.97\%} & \textbf{0.5\%}\\
\hline
\end{tabular}
\end{table*}

@@

The GLEAM survey covers 72.3--230.8 MHz split into 5 bands of 30.72 MHz. The GLEAM observations are made in drift-scan mode, and the 5 bands are observed one by one in 5 subsequent snapshots.

@@

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/2014-03-17-dvb-stddevs}\vspace{-1cm}
\caption{..}
\label{fig:dvb-stddevs}
\end{center}
\end{figure*}

\noindent\begin{figure}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/lognlogs-residual}
\caption{Log N log S for residuals}
\label{fig:lognlogs-residuals}
\end{center}
\end{figure}

\noindent\begin{figure}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/lognlogs-rfi}
\caption{Log N log S for RFI }
\label{fig:lognlogs-rfi}
\end{center}
\end{figure}
